\section{Feedback from Peer Review}
We discussed our project proposal with Yanqing Peng and Yuwei Wang. While they
found our project scope is adequate for a course project and our story make
sense, we received the following valuable comments from them.

\begin{enumerate}[1.]
    \item {\bfseries
        Though the design gives a global picture of how bank failures are
        distributed over time and space, it is hard to pinpoint a specific
        bank of interest. The design does provide detailed information of a
        bank by hovering over a dot on the map, a bank of interest might not
        be known by its headquarter location. Rather it's more likely to be
        the bank name.}

    We will add a search box that allows searching specific banks. Those banks
    whose names partially match the search string will be highlighted on the
    map.

    \item {\bfseries
        The design lacks the usage of colors.
    }

    We plan to use a color scale on the dots of the map to indicate the size
    of it (TBD, either using the total deposits or the total assets).

    \item {\bfseries
        The bar chart is a bit confusing. It's not clear that it is linked to
        the line chart and the order of x-axis is not specified.
    }

    We will clarify the linking by very obvious chart titles/axis titles. We
    will also optimize the layout so that the linking is easy to identify.
\end{enumerate}

We appreciate Yanqing and Yuwei's inspiring and high-quality comments. We
both find them essential to make our visualization easier to explore and more
self-explanatory. We have added the fixes to our implementation plan.

